Matching Bullets

### 2015-12-09 imaging-paper.Rnw
caught another land/part

\hh{XXX add parameter estimates? $\hat{r} \approx 4500$ - indicating a 9 mm bullet, amount of degrees covered by land?  }
The scatterplot in Figure~\ref{fig:residual} shows the residuals of such a fit. The residuals are dominated, as expected, by the grooves, which show up as large positive residuals. For a surface cross cut at $x = 100$ there is a residual circular structure that does not show up for all cross sections.

@@

%' 
%' <<rforest, echo=FALSE>>=
%' library(randomForest)
%' rtrees <- randomForest(factor(match)~., data=CCFs[,includes], ntree=1000)
%' CCFs$forest <- predict(rtrees)
%' importance(rtrees)
%' @
%'

>>>>

The scatterplot in Figure~\ref{fig:residual} shows the residuals of such a fit.
\hh{In this instance, the radius is estimated as $\hat{r} = \Sexpr{pars$radius}\mu m = \Sexpr{pars$radius/1000}mm$, which is consistent with a 9 mm bullet fired in a Ruger P-85. }
The residuals are dominated, as expected, by the grooves, which show up as large positive residuals. For a surface cross cut at $x = 100$ there is a residual circular structure that does not show up for all cross sections.

-%\hh{XXX add parameter estimates? $\hat{r} \approx 4500$ - indicating a 9 mm bullet, amount of degrees covered by land?  }

@@

%' 
%' <<rforest, echo=FALSE>>=
%' library(randomForest)
%' rtrees <- randomForest(factor(match)~., data=CCFs[,includes], ntree=300)
%' CCFs$forest <- predict(rtrees)
%' importance(rtrees)
%' @
%'
